\textbf{Learning semi-Markovian DAGs with flow-based VAE}

### 2023-12-02 Tex/paper.tex
tex

\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{fig/model.png}
    \caption{Architecture of the proposed model.}
    \label{diagram}
\end{figure}

@@

\paragraph*{Datasets} Random graph datasets are generated using the following procedure. First, we generate a random directed acyclic graph using the Erdős–Rényi model. In Section 5.1, we conduct experiments where the noise variables follows a multivariate Gaussian distribution with a non-diagonal covariance matrix. We randomly select a given proportion of edges and make them bidirectional. Then, we generate a corresponding random covariance matrix and generate multivariate Gaussian data using that covariance matrix. We generate 5000 samples for each graph. For the size of the graph, we use 10, 20, 30, and 50 nodes. For the proportion of bidirectional edges, we use 0, 0.1, 0.3, 0.5, and 0.8. In Section 5.2, we consider the case where the noise variables follow not only an independent Gaussian distribution but also independent Laplace and exponential distributions.\\

@@

Here is the introduction of our experiment on dependent noise case

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{fig/model.png}
    \caption{Architecture of the proposed model.}
    \label{diagram}
\end{figure}

@@

\paragraph*{Datasets} Random graph datasets are generated using the following procedure. First, we generate a random directed acyclic graph using the Erdős–Rényi model. In Section 5.1, we consider the case where the noise variables follow not only an independent Gaussian distribution but also independent Laplace and exponential distributions. In Section 5.2, we conduct experiments where the noise variables follows a multivariate Gaussian distribution with a non-diagonal covariance matrix. We randomly select a given proportion of edges and make them bidirectional. Then, we generate a corresponding random covariance matrix and generate multivariate Gaussian data using that covariance matrix. In both sections, we generate 5000 samples for each graph. For the size of the graph, we use 10, 20, 30, and 50 nodes. For the proportion of bidirectional edges, we use 0.1, 0.3, 0.5, and 0.8. \\

@@

First, when the proportion of bidirectional edges is fixed to 0.5, we compare the performance of our method with DAG-GNN. The results are shown in Figure \ref*{SHD_FDR_prop50}. Our method outperforms DAG-GNN in terms of both SHD and FDR. Also, at the node size of 20, our method has shown stable training, which results a huge difference in SHD and FDR. The example of estimated graphs of each method is shown in Figure \ref*{example_graphs}. The estimated graph from DAG-GNN(third column) has much more edges than the true graph(first column), while our method(second column) has much similar number of edges with the true graph.\\

\begin{figure}[H]
    \centering
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{fig/SHD_dependence_50.pdf}
        \caption{SHD with dependence proportion 0.5}
        \label{SHD_prop50}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{fig/FDR_dependence_50.pdf}
        \caption{FDR with dependence proportion 0.5}
        \label{FDR_prop50}
    \end{subfigure}
    \caption{SHD and FDR with dependence proportion 0.5}
    \label{SHD_FDR_prop50}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{fig/comparison_dep_20_50_seed41.pdf}
    \caption{Example of estimated graphs with node size 20 and dependence proportion 0.5}
    \label{example_graphs}
\end{figure}

Next, we compare the performance of two methods with different proportions of bidirectional edges. The results are shown in Figure \ref*{SHD_FDR_node10_20}. When the node size is 10, DAG-GNN outperforms our method in terms of SHD. However, when the node size is 20, our method outperforms DAG-GNN in terms of both SHD and FDR.\\

\begin{figure}[H]
    \centering
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{fig/SHD_dependence_10_DAG_threshold0.3.pdf}
        \caption{SHD with node size 10}
        \label{SHD_node10}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{fig/FDR_dependence_10_DAG_threshold0.3.pdf}
        \caption{FDR with node size 10}
        \label{FDR_node10}
    \end{subfigure}
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{fig/SHD_dependence_20_DAG_threshold0.3.pdf}
        \caption{SHD with node size 20}
        \label{SHD_node20}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{fig/FDR_dependence_20_DAG_threshold0.3.pdf}
        \caption{FDR with node size 20}
        \label{FDR_node20}
    \end{subfigure}
    \caption{SHD and FDR with dependence proportion 0.1, 0.3, 0.5, and 0.8}
    \label{SHD_FDR_node10_20}
\end{figure}
